The Exoplanet Orbit Database \textsc{II}: 2014 updates

### 2014-03-21 draft/ms.tex
Modify mass ratio cut q<0.024 to q<0.023, ie. 24Mjup/Msun.

The scope of the EOD has expanded, and there are three major changes
from what was described in \cite{Wright2011}. Previously, we only
included exoplanets orbiting the ``normal stars", but now we are not
limiting the type of host stars (e.g. we included exoplanets orbiting
neutron stars). Furthermore, in \cite{Wright2011}, we only had
exoplanets that were discovered by the RV and transit methods in the
EOD, but now we also have planets discovered via timing. For the future, exoplanets discovered by any other methods with robust detections and good orbital parameters will also be included in the
EOD. Previously, we required the planets to be smaller than 24 \mjup\ but now we require the mass ratio to be smaller than 24 \mjup$/\msun$.

@@

\begin{itemize}
\item Imaging planets:
\begin{enumerate}
\item Planet-star mass ratio $q < 0.024$ ($< 24\ $\mjup\ for a solar
  mass star); and in general we require ($q+\sigma_q$) $< 0.024$,
  where $\sigma_q$ is the uncertainty in $q$.
\item SEP $<$ 100 AU $\times$ ($M_*/M_\odot$), where SEP is the
  semi-major axis a if a is known, and the projected separation
  otherwise.
\item Confidently detected: the detection is clearly of a real
  astrophysical source, and will unlikely later be found to have been
  spurious.
\item Confidently bound: in opinion of the QUACBED the object will not
  be later found to be unbound or a chance alignment.

\end{enumerate}
\item Microlensing planets:\\
  We accept microlensing planets that appear in refereed journals as
  having unambiguously planetary masses (planet host mass ratio,
  $q<0.024$). In cases of ambiguity, we consult with QUACBED.

>>>>

The scope of the EOD has expanded, and there are three major changes
from what was described in \cite{Wright2011}. Previously, we only
included exoplanets orbiting the ``normal stars", but now we are not
limiting the type of host stars (e.g. we included exoplanets orbiting
neutron stars). Furthermore, in \cite{Wright2011}, we only had
exoplanets that were discovered by the RV and transit methods in the
EOD, but now we also have planets discovered via timing. For the
future, exoplanets discovered by any other methods with robust
detections and good orbital parameters will also be included in the
EOD. Previously, we required the planets to be smaller than 24
\mjup, but now we require the mass ratio to be smaller than 24
\mjup$/\msun$ ($< 0.023)$.

@@

\begin{itemize}
\item Imaging planets:
\begin{enumerate}
\item Planet-star mass ratio $q < 0.023$ ($< 24\ $\mjup\ for a solar
  mass star); and in general we require ($q+\sigma_q$) $< 0.023$,
  where $\sigma_q$ is the uncertainty in $q$.
\item SEP $<$ 100 AU $\times$ ($M_*/M_\odot$), where SEP is the
  semi-major axis a if a is known, and the projected separation
  otherwise.
\item Confidently detected: the detection is clearly of a real
  astrophysical source, and will unlikely later be found to have been
  spurious.
\item Confidently bound: in opinion of the QUACBED the object will not
  be later found to be unbound or a chance alignment.

\end{enumerate}
\item Microlensing planets:\\
  We accept microlensing planets that appear in refereed journals as
  having unambiguously planetary masses (planet host mass ratio,
  $q<0.023$). In cases of ambiguity, we consult with QUACBED.
